---
title: "Datavizualization Project: THE MEDICAL APPOINTMENT NO-SHOW"
author: "Charith Musku, Bhargav Kandlagunta, Bhagya Reddy"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Load the required packages.
suppressMessages(library(ggpubr))
suppressMessages(library(ggplot2))
suppressMessages(library(plyr))
suppressMessages(library(dplyr))
suppressMessages(library(reshape2))
suppressMessages(library(Hmisc))
suppressMessages(library(GGally))
suppressMessages(library(lubridate))
suppressMessages(library(stringr))
suppressMessages(library(scales))
suppressMessages(library(corrplot))
suppressMessages(library(GGally))
suppressMessages(library(gridExtra))
suppressMessages(library(grid))
suppressMessages(library(readr))
suppressMessages(library(caret))
suppressMessages(library(MASS))
```

## Read the data
```{r}
recordData <- read.csv('NoShowDatabase.csv',header = TRUE)
str(recordData)
```
```{r}
summary(recordData)
```
##Data Preprocessing
```{r}
#For column Age remove the negative values
recordData <- filter(recordData, Age > 0)

#Change the format of AppointmentRegistration column
recordData$AppointmentRegistration = ymd_hms(recordData$AppointmentRegistration)

#Change the format of ApointmentData and extract date,month and year information
recordData$ApointmentData <- as.Date(gsub(pattern = "[A-Z]", replacement = " ",x = recordData$ApointmentData))
recordData <-transform(recordData, month = format(ApointmentData, "%m"))
recordData <- transform(recordData, year = format(ApointmentData, "%Y"))
recordData <- transform(recordData, day = format(ApointmentData, "%d"))
recordData$year <- as.integer(as.character(recordData$year))
recordData$month <- as.integer(as.character(recordData$month))
recordData$day <- as.integer(as.character(recordData$day))

#Create a new column as int_status
recordData$int_status <- as.numeric(factor(recordData$Status, levels=c("Show-Up", "No-Show"),labels = c(0, 1)))

#Awaiting time is converted to waiting time by changing it into positive values.
recordData$AwaitingTime = -(recordData$AwaitingTime)

str(recordData)

```

##Correlation Matrix
```{r}
corr_mat = cor(recordData[,c("int_status","Age","Diabetes","Alcoolism","Handcap","HiperTension","Smokes",
                             "Scholarship","Tuberculosis","AwaitingTime","month","year","day","Sms_Reminder")])
colnames(corr_mat) <- c("STATUS","Age", "Diabetes", "Alcoholism","Handicap","HyperTension" , "Smokes",
                        "Scholarship","Tuberculosis", "Awaiting.Time", "Appointment.Month", 
                        "Appointment.Year","Appointment.Day","SMS.Reminder")
correlation_matrix_plot = ggcorr(corr_mat,label=TRUE,hjust = 0.9, size = 3, color = "black", layout.exp = 2)+
  labs(title = "Correlation Matrix", subtitle = "Correlation of Factors w.r.t \"Status\"variable")
correlation_matrix_plot
```


##Vizualization Plots

##Plot 1:

###Age vs Absence rate:
```{r}
#filter age<90 and group by Age
filter_age = filter(recordData, Age<90)
data_age<-group_by(filter_age, Age)
data_age <- dplyr::summarize(data_age,absence_rate = mean(int_status),n = n())

#Scatter plot and trend
ggplot(aes(x = Age, y = absence_rate-1), data = data_age) + geom_smooth(method = "loess")+
  geom_point(size = 1)+labs(x='Age (years)',y='No-Show Rate %',title = 'Age of Patient vs No-show rate') +
  scale_x_continuous(breaks=seq(0,100,5))
```

```{r}
#creating bins of Age and plotting the Absence rate vs Age bins:
data_age$age_bucket <- cut(data_age$Age, breaks= seq(0,90, 5), include.lowest=TRUE)
data_agebucket <- group_by(data_age, age_bucket)
data_agebucket <- dplyr::summarize(data_agebucket,absence_rate = mean(absence_rate-1),n = n())

plot_age=ggplot(aes(x = age_bucket, y = 100*absence_rate),data= data_agebucket) +
  geom_bar(stat='identity', color='black',fill = 'lightblue', lwd = 0.8, width=1) +
  theme(axis.text.x=element_text(angle = 60, hjust=1))+ scale_y_continuous(breaks=seq(-40, 40, 10))+
  labs(x = 'Age Group', y = 'No-Show Rate in %',title ='Age Group vs No-Show Rate')
plot_age
```

##Plot 2:
###Gender vs Absence Rate:
```{r}
data_gender <- group_by(recordData, Gender)
data_gender <- dplyr::summarize(data_gender,absence_rate = mean(int_status),n = n())
labels = c('Male', 'Female')
data_gender$gender_name <- labels
data_gender$gender_name <- factor(data_gender$gender_name,levels=unique(data_gender$gender_name))

ggplot(data_gender, aes(x = gender_name, y = 100*(absence_rate-1))) + geom_bar(stat = "identity",width = 0.5,color='black',fill = "lightblue" )+ labs(x = 'Gender', y = 'Absence Rate %',title='Gender vs Absence Rate')
```

##Plot3:

### No-show rate vs Reg_hour :
```{r}
data_time <- group_by(recordData, RegistrationHour=hour(AppointmentRegistration)) 
data_time<- dplyr::summarize(data_time,absence_rate = mean(int_status),n = n())
ggplot(data_time,aes(x=RegistrationHour, y=100*(absence_rate-1)))+geom_bar(stat="identity",fill="blue")+
  scale_fill_discrete("Registration Hour")+xlab("Registration Hour")+ylab("Absence Rate in %")+
  ggtitle("Absence Rate vs Registration hour in a day")
```
```{r}
ggplot(recordData, aes(x=hour(AppointmentRegistration),fill=hour(AppointmentRegistration)))+
  geom_histogram(fill="blue",binwidth= 0.5)+xlab("Registration Hour")+
  ylab("Count of Appointments")+ggtitle("Count of Appointments w.r.t Registration hour in a day")
```

##Plot4:
###Day of the week vs Absence Rate:
```{r}
data_weekday <-recordData %>% group_by(DayOfTheWeek, Gender) %>% dplyr::count(Status)

#Taking the information from week day counting the Staus and assigning to 
data_weekday <- tidyr::spread(data_weekday, key = Status, value = n)
colnames(data_weekday) <- c("DayOfTheWeek", "Gender", "Noshow", "Show")
data_weekday <- data_weekday %>% mutate(absenceRate = round(Noshow / (Noshow + Show), digits = 3))
data_weekday$Gender <- factor(data_weekday$Gender, levels = c("M", "F"))
week_day = data_weekday %>% group_by(DayOfTheWeek) %>% summarise(absenceRate = mean(absenceRate))
ggplot(week_day, aes(x = DayOfTheWeek, y = 100*absenceRate))+ geom_bar(stat = "identity", fill = "blue") +
  scale_x_discrete(limits = c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday"),
                   labels = c("Mon", "Tues", "Wed", "Thurs", "Fri", "Sat", "Sun")) +
  ggtitle("Day of the week vs Absence Rate") + xlab("Day of the week")+ylab("No Show rate in %")
```

```{r}
recordData$DayOfTheWeek <- factor(recordData$DayOfTheWeek,levels=c("Monday","Tuesday","Wednesday","Thursday","Friday","Saturday","Sunday"))

plot1 = ggplot(recordData,aes(x=DayOfTheWeek,fill=DayOfTheWeek))+geom_bar(fill = "blue")+
  xlab("Day of the week")+ylab("Count")+ggtitle("Count of Appointments vs Days of the week")

plot2 = ggplot(recordData, aes(x=DayOfTheWeek,fill=Status))+geom_bar(stat="count",position="fill")+
  xlab("Day of the week")+ylab("Proportion of Show and No-Show")+ 
  ggtitle("Proportion of Show and No-show w.r.t days of the week")
grid.arrange(plot1,plot2)
```

##Plot 5:
###Status vs Absence Rate:
```{r}
plot_status = ggplot(recordData)+geom_bar(aes(x = Status,fill = Status))+ggtitle("Imbalance in Status variable")
plot_status
```

##Plot 6:
###Behavioral patterns in patients count:
```{r}
part1 <- ggplot(recordData)+geom_bar(aes(Scholarship, fill = Scholarship))+ylab('Count')+xlab("Scholarship")+
  scale_x_discrete(limits = c(0,1),labels = c("No","Yes"))+scale_y_continuous(limits = c(0,300000),label = unit_format(unit="K", scale =1e-3))

part2 <- ggplot(recordData)+geom_bar(aes(HiperTension, fill =HiperTension))+ylab('Count')+xlab("HyperTension")+
  scale_x_discrete(limits = c(0,1),labels = c("No","Yes"))+scale_y_continuous(limits = c(0,300000),label = unit_format(unit ="K",scale =1e-3))

part3 <- ggplot(recordData)+geom_bar(aes(Diabetes, fill = Diabetes))+ylab('Count')+xlab("Diabetes")+
  scale_x_discrete(limits = c(0,1),labels = c("No","Yes"))+scale_y_continuous(limits = c(0,300000),label =unit_format(unit ="K", scale =1e-3))

part4 <- ggplot(recordData)+geom_bar(aes (Alcoolism, fill =  Alcoolism))+ylab('Count')+xlab("Alcoholism")+
  scale_x_discrete(limits = c(0,1),labels = c("No","Yes"))+scale_y_continuous(limits = c(0,300000),label =unit_format(unit ="K", scale =1e-3))

part5 <- ggplot(recordData)+geom_bar(aes( Handcap, fill = Handcap))+ylab('Count')+xlab("Handicap")+
  scale_x_discrete(limits = c(0,1,2,3,4))+scale_y_continuous(limits = c(0,300000),label = unit_format(unit = "K", scale =1e-3))

part6 <- ggplot(recordData)+geom_bar(aes(Sms_Reminder, fill = Sms_Reminder))+ylab('Count')+xlab("Sms_Reminder")+
  scale_y_continuous(limits = c(0,300000),label = unit_format(unit = "K", scale =1e-3))

part7 <- ggplot(recordData)+geom_bar(aes(Smokes, fill = Smokes))+ylab('Count')+xlab("Smokes")+
  scale_x_discrete(limits = c(0,1),labels = c("No","Yes"))+scale_y_continuous(limits = c(0,300000),label = unit_format(unit="K", scale =1e-3))

part8 <- ggplot(recordData)+geom_bar(aes(Tuberculosis, fill = Tuberculosis))+ylab('Count')+xlab("Tuberculosis")+
  scale_x_discrete(limits = c(0,1),labels = c("No","Yes"))+scale_y_continuous(limits = c(0,300000),label = unit_format(unit="K", scale =1e-3))

gridformat = ggarrange(part1,part2,part3,part4,part5,part6,part7,part8, nrow = 4,ncol =2)
plot_behaviours = annotate_figure(gridformat, top = text_grob("Number of Patients in each marker", color = 
                                                                "black", size = 13))
plot_behaviours
```

###Behavioral patterns in patients proportion:
```{r}
plot1 <- ggplot(recordData)+geom_bar(aes(Scholarship, fill = Status), position = position_fill())+
    ylab('Proportion')+scale_x_discrete(limits = c(0,1),labels = c("No","Yes"))+xlab("Scholarship")+theme(legend.position="none")
plot2 <- ggplot(recordData)+geom_bar(aes(HiperTension, fill =Status), position = position_fill())+
    ylab('Proportion')+scale_x_discrete(limits = c(0,1),labels = c("No","Yes"))+xlab("HyperTension")+theme(legend.position="none")
plot3 <- ggplot(recordData)+geom_bar(aes(Diabetes, fill = Status), position = position_fill())+
    ylab('Proportion')+scale_x_discrete(limits = c(0,1),labels = c("No","Yes"))+xlab("Diabetes")+theme(legend.position="none")
plot4 <- ggplot(recordData)+geom_bar(aes (Alcoolism, fill =  Status), position = position_fill())+
    ylab('Proportion')+scale_x_discrete(limits = c(0,1),labels = c("No","Yes"))+xlab("Alcoholism")+theme(legend.position="none")
plot5 <- ggplot(recordData)+geom_bar(aes( Handcap, fill = Status), position = position_fill())+
    ylab('Proportion')+xlab("Handicap")+theme(legend.position="none")
plot6 <- ggplot(recordData)+geom_bar(aes(Sms_Reminder, fill = Status), position = position_fill())+
    ylab('Proportion')+xlab("Sms_Reminder")+theme(legend.position="none")
plot7 <- ggplot(recordData)+geom_bar(aes( Smokes, fill = Status), position = position_fill())+
    ylab('Proportion')+scale_x_discrete(limits = c(0,1),labels = c("No","Yes"))+xlab("Smokes")+theme(legend.position="none")
plot8 <- ggplot(recordData)+geom_bar(aes( Tuberculosis, fill = Status), position = position_fill())+
    ylab('Proportion')+scale_x_discrete(limits = c(0,1),labels = c("No","Yes"))+xlab("Tuberculosis")

figure <- ggarrange(plot1,plot2,plot3,plot4,plot5,plot6,plot7,plot8, nrow = 4, ncol=2, common.legend = TRUE, legend="right")

# Annotate the figure by adding a common labels
plot_behaviours_proportions = annotate_figure(figure, top = text_grob("Behavioral Patterns in Patients",color = 
                                                                        "black",size = 13))
plot_behaviours_proportions
```

##Plot 7:
###SMS Reminders vs No-show Rate
```{r}
data_sms <- group_by(recordData, Sms_Reminder)
data_sms <- dplyr::summarize(data_sms, absence_rate = mean(int_status),n = n())
ggplot(data_sms,aes(x=Sms_Reminder,y=100*(absence_rate-1)))+geom_bar(stat='identity',color='black',fill='blue')+labs(x = 'Number of SMS Reminders', y = 'No-show Rate %',title = 'Number of SMS Reminders vs No-Show Rate')+
  scale_y_continuous(breaks=seq(0, 40, 10))
```

```{r}
ggplot(recordData, aes(x=Sms_Reminder,fill=Status))+geom_bar(stat="count",position="fill")+
  xlab("Number of SMS Reminders")+
  ylab("Proportion of Show and No-Show")+ggtitle("Proportion of Show and No-show w.r.t no.of SMS Reminders")
```

#Plot 8:
###Absence rate vs Age by Text Reminders
```{r}
#Use the filter_age where we filtered age<90
ggplot(aes(x = Age, y = Sms_Reminder), data = filter_age)+geom_line(stat='summary',fun.y = mean, color='blue') +
  labs(x ='Age(years)',y='Number of SMS Reminders for each appointment',title='Average SMS Reminders vs Age' ) +
  scale_x_continuous(breaks= seq(0,90, 10))
```

```{r}
filter_sms <- filter(recordData, Sms_Reminder<2)
data_texts <- group_by(filter_sms, Age)
data_texts <- filter(data_texts, Age < 90)
data_texts$Sms_Reminder <- factor(data_texts$Sms_Reminder)
plot_sms_age= ggplot(aes(x = Age, y = 100*(int_status-1)),data = data_texts)+
  geom_line(aes(color=Sms_Reminder), stat = 'summary', fun.y = mean, lwd = 1.2)+
  labs(x = 'Age (yrs)', y = 'Absence Rate %',title='Age by Text Reminders vs Absence Rate' ) + 
  scale_color_manual(name='Number of SMS Reminders',values=c('red','blue', 'slategray4'))
plot_sms_age
```

##Plot 9:
###Waiting Time vs No-show rate
```{r}
#Waiting time behaviour
data_waittime <- group_by(recordData, AwaitingTime)
data_waittime <- dplyr::summarize(data_waittime,absence_rate = mean(int_status),n = n())

# No show rate vs age scatter plot.
ggplot(aes(x = AwaitingTime, y = 100 * (absence_rate-1)), data = data_waittime) + geom_point(color='black') + 
  geom_smooth(method ="loess")+ labs(x = 'Wait(days)',y = 'No-show Rate %',title='No-show Rate vs Waiting Time')
```

```{r}
#Filtering out the ages less than 90 days
data_waittime <- filter(data_waittime, AwaitingTime< 90)

#Cutting the wait time into bins of 10 days each like the age.
data_waittime$wait_bucket<-cut(data_waittime$AwaitingTime,breaks = seq(0,90,10),include.lowest = TRUE)
data_waittime_bucket <- group_by(data_waittime, wait_bucket)
data_waittime_bucket <- dplyr::summarize(data_waittime_bucket,absence_rate = mean(absence_rate-1),n = n())

#Relative absence rate is calculated as the trend in the absolute absence rate is not significant.
data_waittime_bucket$rel_rate <- with(data_waittime_bucket, 100 *(absence_rate - mean(absence_rate)) / mean(absence_rate))

# Graph the relative absence rate for each age bucket
plot_waittime = ggplot(aes(x = wait_bucket, y = rel_rate),data = data_waittime_bucket) + 
  geom_bar(stat='identity', color='black',fill='lightblue',lwd = 0.8, width = 1) +
  scale_y_continuous(breaks=seq(-20, 50, 5)) + 
  labs(x='Wait Time Group(days)',y='Relative No-Show Rate in %',title='Waiting Time  Group vs Relative No-Show Rate')
plot_waittime
```

##Plot 10:

###No show rate vs month
```{r}
##Month plot 1:
data_month <- group_by(recordData, month)
data_month <- dplyr::summarize(data_month,absence_rate = mean(int_status),n = n())

labels = c('Jan', 'Feb', 'Mar', 'Apr', 'May', 'Jun', 'Jul' ,'Aug', 'Sep','Oct', 'Nov' , 'Dec')
data_month$month_label <- labels
data_month$month_label <- factor(data_month$month_label,levels=unique(data_month$month_label))
plot_month= ggplot(data_month, aes(x = month_label, y = 100*(absence_rate-1))) + 
  geom_point(color = 'red', size = 1.8) + geom_line(group =1, color = 'blue')+
  labs(x = 'Appointment Month', y = 'Absence Rate %',title='Absence Rate vs Appointment Month')
plot_month 
```

```{r}
data_month <-recordData %>% group_by(month, Gender) %>% dplyr::count(Status)

##Month plot 2
data_month <- tidyr::spread(data_month, key = Status, value = n)
colnames(data_month) <- c("month", "Gender", "Noshow", "Show")
data_month <-data_month %>% mutate(absenceRate = round(Noshow / (Noshow + Show), digits = 3))

data_month %>%group_by(month) %>% summarise(absenceRate = mean(absenceRate))%>%
ggplot(aes(x = month, y = 100*absenceRate)) + geom_bar(stat = "identity", fill = "blue") +
  scale_x_discrete(limits = c(1, 2, 3, 4, 5, 6, 7,8,9,10,11,12), 
                   labels = c("Jan", "Feb", "Mar", "Apr", "May","Jun", "Jul", "Aug","Sep","Oct","Nov","Dec")) +
  xlab("Month of the year") + ylab("No-Show Rate in %") + ggtitle("No-Show Rate Against month in a year") 
```

##Plot 11:
###Absence rate vs Appointment day
```{r}
data_day <- group_by(recordData, day)
data_day <- dplyr::summarize(data_day,absence_rate = mean(int_status), n = n())
plot_day= ggplot(aes(x = day, y = 100*(absence_rate-1)), data = data_day) + geom_point(color = 'red')  + 
  labs(x = 'Day of Appointment',y = 'No-Show Rate in %',title='No-Show Rate vs Appointment Day') +
  scale_x_continuous(breaks=seq(1,31,1)) + geom_line(color='blue')+
  theme(axis.text.x=element_text(angle = 60, hjust=1))
plot_day
```


##Research Questionnaire:

## Q1: What factors are most likely to determine whether a patient shows up to their scheduled doctor's appointment?
```{r}
correlation_matrix_plot
```
```{r}
plot_age
```

```{r}
plot_waittime
```

```{r}
plot_month
```
```{r}
plot_day
```

```{r}
plot_sms_age
```

## Q2: How is the absence/no-show to a scheduled appointment dependent on the general characteristics and behavior patterns of the patient?
```{r}
plot_behaviours
```

```{r}
plot_behaviours_proportions
```

```{r}
plot_status
```

## Q3: Can we predict whether a patient would show up or not by taking the aforementioned variables as explanatory variables into consideration?

###Clean and preprocess the data based on above analysis for building Models
```{r}
#load data again
recordData <- read.csv('NoShowDatabase.csv',header = TRUE)
recordData.Status <- recordData$Status

#Remove AppointmentRegistration & ApointmentData columns
recordData <- recordData[,-c(3,4)]

#Adjust the age
recordData <- filter(recordData, Age >= 0 & Age<90)

data_age<-group_by(recordData, Age)
recordData$age_bin <- cut(data_age$Age,breaks= seq(0,90,5), include.lowest=TRUE)
recordData$age_bin <- as.factor(recordData$age_bin)

#Change Awaiting time to positive
recordData$AwaitingTime = -(recordData$AwaitingTime)

recordData<-recordData[,-c(1)]
recordData[sapply(recordData, is.numeric)] <- lapply(recordData[sapply(recordData, is.numeric)],as.factor)
recordData$AwaitingTime<-as.numeric(recordData$AwaitingTime)

data_sample <- recordData
data_sample <-as.data.frame(predict(dummyVars(~.,data = data_sample,levelsOnly= FALSE),newdata = data_sample))
data_sample$Status<-recordData$Status
data_sample<-data_sample[,-c(10,11)]
data_sample <-na.omit(data_sample)
```

###Partition data into Training and Testing data
```{r}
set.seed(100)
partition <-createDataPartition(data_sample$Status,p=0.75,list=FALSE)
data_train <-data_sample[partition,]
data_valid <-data_sample[-partition,]
data_train_status <- data_train$Status
data_valid_status<-data_valid$Status
```

##Model 1
```{r}
data_model.1 <- glm(Status~., data = data_train, family = binomial("logit"))
summary(data_model.1)
```

##Model 1 Prediction Results
```{r}
#Hyper parameter tuning the threshold probability variable
valid_set_probs = predict(data_model.1,data_valid,type = "response")
x = c(0.4,0.45,0.5,0.55,0.6,0.65,0.7)
vector = c()
for(val in x){
data_valid$prediction_val<-ifelse(valid_set_probs<val,"No-Show","Show-Up")
data_valid$prediction_val <-as.factor(data_valid$prediction_val)
ConMatrix <-table(data_valid_status,data_valid$prediction_val)
print(ConMatrix)
accuracy = (sum(diag(ConMatrix))/sum(ConMatrix))*100
print(paste("accuracy is",accuracy))
print(paste("Probability is",val))
vector <- c(vector, accuracy)
}
```

```{r}
data.frame(x,vector) %>% ggplot(aes(x = x,y= vector ))+geom_point(color = "red")+geom_line(color = "blue")+xlab("Threshold probabilities")+ylab("Accuracies")+ggtitle("Accuracies vs Threshold probabilities for Model 1")
```

## Final Model 1
```{r warning=FALSE}
#Final Model 1
print(paste("The final confusion matrix after the hyper parameter tuning Model 1:"))
data_valid$prediction<-ifelse(valid_set_probs<0.6,"No-Show","Show-Up")
data_valid$prediction <-as.factor(data_valid$prediction)
ConfMatrix <-table(data_valid_status,data_valid$prediction)
ConfMatrix
print(paste("The final test accuracy is ",(sum(diag(ConfMatrix))/sum(ConfMatrix))*100,"%"))

```

```{r warning=FALSE}
library(pROC)
preds_1=predict(data_model.1,data_valid, type="response")
roc1=roc(data_valid_status ~ preds_1)
plot(roc1, main = "Model 1 ROC plot")

```


#Model 2 is made based on the important features from the summary of the Model 1

```{r warning=FALSE}
data_train<-data_train[,-c(2,3,6,7,8,9,10,11,13,14,15,16,17,18,19,20,22,24,25,26,27,28,29,40,41,42,43,44,47,48,49)]
data_model.2 <- glm(data_train_status~., data = data_train, family = binomial("logit"))
summary(data_model.2)
```

#Model 2: Predictions and Hyperparameter tuning:

```{r warning=FALSE}
#Hyper parameter tuning the threshold probability variable
valid_set_probs = predict(data_model.2,data_valid,type = "response")
x.2 = c(0.4,0.45,0.5,0.55,0.6,0.65,0.7)
vector.2 = c()
for(val in x.2){
data_valid$prediction_val_2<-ifelse(valid_set_probs<val,"No-Show","Show-Up")
data_valid$prediction_val_2 <-as.factor(data_valid$prediction_val_2)
ConMatrix <-table(data_valid_status,data_valid$prediction_val_2)
print(ConMatrix)
acc.2 = (sum(diag(ConMatrix))/sum(ConMatrix))*100
print(paste("Accuracy is",acc.2))
print(paste("Probability is",val))
vector.2 <- c(vector.2, acc.2)
}

data.frame(x.2,vector.2) %>% ggplot(aes(x = x.2,y= vector.2 ))+geom_point(color = "red")+geom_line(color = "blue")+xlab("Threshold probabilities")+ylab("Accuracies")+ggtitle("Accuracies vs Threshold probabilities for Model 1")

```

## Final Model 2

```{r warning=FALSE}

#Final Model 2
print(paste("The final confusion matrix after the hyper parameter tuning Model 2:"))
data_valid$prediction_2<-ifelse(valid_set_probs<0.6,"No-Show","Show-Up")
data_valid$prediction_2 <-as.factor(data_valid$prediction_2)
ConfMatrix.2 <-table(data_valid_status,data_valid$prediction_2)
ConfMatrix.2
print(paste("The final test accuracy is ",(sum(diag(ConfMatrix.2))/sum(ConfMatrix.2))*100,"%"))

```

```{r warning=FALSE}
library(pROC)
preds_2=predict(data_model.2,data_valid, type="response")
roc2=roc(data_valid_status ~ preds_2)
plot(roc2, main = "Model 2 ROC plot")
```

#Balancing the data:

```{r warning=FALSE}
set.seed(100)
showup_data <-filter(data_sample, Status == 'Show-Up')
no_showup_data <- filter(data_sample, Status == 'No-Show')
show_up_50 <- showup_data %>% sample_frac(.5)
balanced_no_show_data = rbind(show_up_50,no_showup_data)
ggplot(data = balanced_no_show_data)+geom_bar(aes(x = Status,fill = Status))+ggtitle("Balance in Status variable")
```

#Dividing into train and test set for the balanced data:

```{r warning=FALSE}
set.seed(100)
data_partition <-createDataPartition(balanced_no_show_data$Status,p=0.75,list=FALSE)
data_train_balanced <-balanced_no_show_data[data_partition,]
data_valid_balanced <-balanced_no_show_data[-data_partition,]
```

#Model 3 with all the features for the balanced data:

```{r warning=FALSE}
Model.3 <- glm(Status~., data = data_train_balanced, family = binomial("logit"))
summary(Model.3)
```
## Final Model 3
```{r warning=FALSE}
valid_set_probs_bal = predict(Model.3,data_valid_balanced,type = "response")
data_valid_balanced$prediction<-ifelse(valid_set_probs_bal<0.65,"No-Show","Show-Up")
data_valid_balanced$prediction <-as.factor(data_valid_balanced$prediction)
print(paste("Confusion matrix for Balanced data model(Model 3)"))
table(data_valid_balanced$Status,data_valid_balanced$prediction)
print(paste("The test accuracy for the balanced data is ",(sum(diag(ConfMatrix))/sum(ConfMatrix))*100,"%"))
```

## Therefore, since Model 2 gives the best accuracy(68.84%) by taking all significant features into account, it can be concluded as the best for predicting the show-up and no-show rates (Refer Documentation Appendix for ROC Curve Comparison).